---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

<!-- badges: start -->
[![license](https://img.shields.io/badge/license-GPL--3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0.en.html)
[![Codecov test coverage](https://codecov.io/gh/lucas-johnson/agreeable/branch/main/graph/badge.svg)](https://codecov.io/gh/lucas-johnson/agreeable?branch=main)
[![R build status](https://github.com/lucas-johnson/agreeable/workflows/R-CMD-check/badge.svg)](https://github.com/lucas-johnson/agreeable/actions)
[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/agreeable)](https://CRAN.R-project.org/package=agreeable)

<!-- badges: end -->

# agreeable

The goal of agreeable is to provide a set of simple tools to assess agreement 
between two matching datasets. The specific use case under which this package was 
developed is to assess the agreement between modeled and observed datasets.

Computations following [Ji and Gallo 2006](https://www.ingentaconnect.com/content/asprs/pers/2006/00000072/00000007/art00006).


## Examples
Here are some of the basic tools made available by agreeable... 

### Simulated data generation:
```{r datagen, results = 'asis', warning=F}
library(agreeable)
library(ggplot2)
library(knitr)

set.seed(123)
observed <- sort(rnorm(500, mean = 300, sd = 75))
predicted_systematic <- sort(rnorm(500, mean = 275, sd = 100))

sds <- c(1, 5, 10, 30, 50, 75, 100, 150)
predicted_unsystematic <- sort(rnorm(500, mean = 300, sd = sds))
```

### 1. AC 
Compute AC (agreement coefficient), ACs (systematic agreement), ACu 
(unsystematic agreement), PUD (percentage of unsystematic difference), and PSD 
(percentage of systematic difference):

Systematic differences dominate:
```{r example_1_systematic, results = 'asis', warning=F}
knitr::kable(
    data.table::data.table(
        AC = ac(observed, predicted_systematic),
        ACs = acs(observed, predicted_systematic),
        ACu = acu(observed, predicted_systematic),
        PUD = pud(observed, predicted_systematic),
        PSD = psd(observed, predicted_systematic)
    )
)
```

Unsystematic (random) differences dominate:
```{r example_1_unsystematic, results = 'asis', warning=F}
knitr::kable(
    data.table::data.table(
        AC = ac(observed, predicted_unsystematic),
        ACs = acs(observed, predicted_unsystematic),
        ACu = acu(observed, predicted_unsystematic),
        PUD = pud(observed, predicted_unsystematic),
        PSD = psd(observed, predicted_unsystematic)
    )
)
```


### 2. GMFR 
Scatter plot with 1:1 and Geometric Mean Functional Relationship (GMFR) lines:

Systematic differences dominate:
```{r example_2_systematic, results = 'asis', warning = F}

# Intercept
a <- a_gmfr(observed, predicted_systematic)

# Slope
b <- b_gmfr(observed, predicted_systematic)

ggplot2::ggplot(data = NULL) + 
    ggplot2::geom_point(
        aes(x = observed, y = predicted_systematic), 
        alpha = 0.7, 
        color = "black"
    ) + 
    ggplot2::geom_abline(aes(slope = 1, intercept = 0, color = "black")) + 
    ggplot2::geom_abline(aes(slope = b, intercept = a, color = "orange")) + 
    ggplot2::scale_color_identity(
        labels=c("1:1", "GMFR"), 
        guide="legend", 
        name = ""
    )
```

Unsystematic (random) differences dominate:
```{r example_2_unsystematic, results = 'asis', warning = F}

a <- a_gmfr(observed, predicted_unsystematic)

# Slope
b <- b_gmfr(observed, predicted_unsystematic)

ggplot2::ggplot(data = NULL) + 
    ggplot2::geom_point(
        aes(x = observed, y = predicted_unsystematic), 
        alpha = 0.7, 
        color = "black"
    ) + 
    ggplot2::geom_abline(aes(slope = 1, intercept = 0, color = "black")) + 
    ggplot2::geom_abline(aes(slope = b, intercept = a, color = "orange")) + 
    ggplot2::scale_color_identity(
        labels=c("1:1", "GMFR"), 
        guide="legend", 
        name = ""
    )
```

## Installation

<!-- You can install the released version of agreeable from [CRAN](https://CRAN.R-project.org) with: -->
There is no released version of agreeable yet. 

<!-- ``` r -->
<!-- install.packages("agreeable") -->
<!-- ``` -->

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("lucas-johnson/agreeable")
```
